### 2020-03-25 korea.tex
one more citation

We analyzed epidemiological data describing the COVID-19 outbreak in South Korea between January 20--March 16, 2020.
Daily number of reported cases in each geographic region was transcribed from press releases by Korea Centers for Disease Control and Prevention (KCDC) \cite{kcdc}.
Partial line lists were transcribed from press releases from KCDC and various local and provincial governments \cite{seoul, busan, gwangju, ulsan, gyeonggi, daegu}.
All data and original reports are stored in a publicly available GitHub repository.

>>>>

We analyzed epidemiological data describing the COVID-19 outbreak in South Korea between January 20--March 16, 2020.
Daily number of reported cases in each geographic region was transcribed from press releases by Korea Centers for Disease Control and Prevention (KCDC) \cite{kcdc}.
Partial line lists were transcribed from press releases from KCDC and various local and provincial governments \cite{seoul, busan, gwangju, ulsan, gyeonggi, daegu, gyeongnam}.
All data and original reports are stored in a publicly available GitHub repository.
